Silent pessimists: researchers' perceptions of malaria eradication

### 2017-12-28 paper.Rmd
update

Many pointed to the failure of the WHO GMP in the 1950s as evidence of the futile nature of eradication programs. Many highlighted that talking about "malaria" as one disease misses the mark, since the different species of parasite and contexts in which they live make elimination in each area very distinct from other areas. "Meta" comments tended to be skeptical of the feasibility of eradication, or to challenge the  notion that it is a meaningful or useful endeavor. Largely, they were prescriptive, advocating for a re-framing of the conversation so that the focus was not on an "arbitrary" goal like eradication, but rather on scaling up control and making region-specific progress.

>>>>

Many pointed to the failure of the WHO GMP in the 1950s as evidence of the futile nature of eradication programs. Some highlighted that talking about "malaria" as one disease misses the mark, since the different species of parasite and contexts in which they live make elimination in each area very distinct from other areas. Comments which "tackled the fundamentals" tended to be skeptical of the feasibility of eradication, or to challenge the  notion that it is a meaningful or useful endeavor. Largely, they were prescriptive, advocating for a re-framing of the conversation so that the focus was not on an "arbitrary" goal like eradication, but rather on scaling up control and making region-specific progress.
